Extended Data

### 2021-10-18 doc/manuscript/Dow_manuscript_Nature.Rmd
methods: use of April as alternative critical temperature window
#82

>>>>

To ensure that patterns were robust under an alternative definition of critical temperature window, and to parallel the monthly time windows used in our tree-ring analysis (detailed below; Fig. `r tree_rings`, `r EDF_tree_ring_figs`), we also ran analyses defining the critical temperature window as the month of April.
This was consistent with the periods identified by *climwin* for ring- and diffuse-porous species groups at both sites, all of which included all or part of April (`r  EDT_mean_growth_parameters`).
